Remotely SST

### 2019-08-06 remote_SST.Rmd
OISST

```{r}
library(tidyverse)
library(plyr)
library(lubridate)
library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(data.table)
library(heatwaveR)
library(viridis)
library(gridExtra)
library(fossil)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ggpubr)
library(ggpubr); theme_set(theme_pubr())# library(devtools)
```

@@

## The nearest SST pixels
Now we apply the FNN (Fast Nearest Neighbor) package to determine the nearesr SST pixel to the insitu collected sites.

load("Data_P1/site_list_sub.Rdata") # Loading the SACTN_overlap dataset which allows me to match it to the OISST data

@@

# Subsetting the OISST data to match the upwelling sites within the in situ collected temperature data
OISST_match <- OISST %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)
# save(OISST_match, file = "Data_P1/OISST_match.RData")

@@

OISST_sites <- OISST_sites %>% 
  dplyr::rename(temp = temp_OISST) %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  drop_na()
# save(OISST_sites, file = "Data_P1/OISST_sites.RData")

## Matching the Insitu data with the OISST SST data
insitu_OISST <- match_func(df = OISST_sites)
```

>>>>

```{r}
library(tidyverse)
library(plyr)
library(lubridate)
library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(data.table)
library(heatwaveR)
library(viridis)
library(gridExtra)
library(fossil)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ggpubr)
library(ggpubr); theme_set(theme_pubr())# library(devtools)
library(FNN)
```

# Plots

```{r}
OISST %>%
  filter(date == min(date)) %>%
  ggplot(aes(x = lon, y = lat)) +
  geom_raster(aes(fill = temp))
```

@@

## The nearest SST pixels
Now we apply the FNN (Fast Nearest Neighbor) package to determine the nearesr SST pixel to the insitu collected sites. 
```{r}
load("~/Documents/Masters_2019/Upwelling_MCS/Data/site_list_sub.Rdata")

@@

# Subsetting the OISST data to match the upwelling sites within the in situ collected temperature data
OISST_match <- OISST %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)
# save(OISST_match, file = "Data/OISST_match.RData")

@@

OISST_sites <- OISST_sites %>% 
  dplyr::rename(temp = temp_OISST) %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  drop_na()
# save(OISST_sites, file = "Data/OISST_sites.RData")
```

```{r}
load("~/Documents/Masters_2019/Upwelling_MCS/Data/OISST_sites.RData")
## Matching the Insitu data with the OISST SST data
insitu_OISST <- match_func(df = OISST_sites)
```
